### 2019-12-09 article_draft.tex
other small edits

As alluded to above, any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $||\cdot||$ to a real value.  To obtain p-values and define the test, compare $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to $\Gamma_\distv(\rvv)$ where $\rvv$ is a random variable with distribution $\distv$. Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.

>>>>

As alluded to above, any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$. While it is not always required, most $\Gamma$ we consider use some norm $||\cdot||$.  To obtain p-values and define the test, compare $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to $\Gamma_\distv(\rvv)$ where $\rvv$ is a random variable with distribution $\distv$. Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.
